Paper 2 !DRAFT! Do not circulate!

### 2014-12-10 Articles/Article_EcolEcon_2014/Paper2.Rnw
Editing graph sizes.

# Load models
REXS1960_Models <- loadPostProcessedData(Source = "REXS1960", kind = "models", dir=pp_path)
IST_Models <- loadPostProcessedData(Source = "IST", kind = "models", dir=pp_path)
Leeds_Models <- loadPostProcessedData(Source = "Leeds", kind = "models", dir=pp_path)
AllModels <- unlist(list(REXS1960_Models, IST_Models, Leeds_Models), recursive=FALSE)
# The function to extract data from the models
extract_data <- function(x, name) {
  # Names are in the form Source.Country.modelType.factor_string
  # Parse various pieces of name
  name_pieces <- strsplit(name, split=".", fixed=TRUE)[[1]]
  Source <- name_pieces[[1]]
  Country <- name_pieces[[2]]
  modelType <- name_pieces[[3]]
  factorString <- name_pieces[[4]]
  # Parse the factorString to get the energyType
  energyType <- parseFactorString(factorString)$energyType
  data.frame(year = (attr(x, which="data"))$Year, resid = resid(x), name=name, Source=Source, Country=Country,
             modelType=modelType, energyType=energyType)
}
residual_data <- leaf_apply(AllModels, extract_data, class=c("CDEmodel", "cesEst", "LINEXmodel"))
# Bind these all in a data frame. 
residuals_df <- do.call(rbind, residual_data)
# Re-order the factors as desired for our graphs.
residuals_df$Source <- as.factor(
  replace(as.character(residuals_df$Source), which(residuals_df$Source=="REXS1960"), "REXS"))
residuals_df$Source <- relevelFactor(residuals_df$Source, levs = c("REXS", "IST", "Leeds"))
residuals_df$energyType <- as.factor(
  replace(as.character(residuals_df$energyType), which(is.na(residuals_df$energyType)), "none"))
residuals_df$energyType <- relevelFactor(as.factor(residuals_df$energyType), levs = energyLevels)
@

@@

<<CD_GDP_Spaghetti_Graphs_UK, fig.pos="H", fig.align='center', fig.width=4, fig.height=4.5, fig.cap="UK Cobb-Douglas fitted models.">>=
cdFittedDataUK <- subset(AllFitted, subset = model=="cd" & Country=="UK")
spaghettiPlot(data=cdFittedDataUK, facet_formula=Source~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1960=1)") +
  scale_x_continuous(breaks=c(1960, 1980, 2000))
@

<<CD_GDP_Spaghetti_Graphs_JP, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="JP Cobb-Douglas fitted models.">>=
cdFittedDataJP <- subset(AllFitted, subset = model=="cd" & Country=="JP")
spaghettiPlot(data=cdFittedDataJP, facet_formula=Source~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1960=1)") +
  scale_x_continuous(breaks=c(1960, 1980, 2000))
@

@@

<<CD_GDP_Spaghetti_Graphs_PT, fig.pos="H", fig.align='center', fig.width=5, fig.height=2.5, fig.cap="PT Cobb-Douglas fitted models.">>=
cdFittedDataPT <- subset(AllFitted, subset = model=="cd" & Country=="PT")
spaghettiPlot(data=cdFittedDataPT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1960=1)") +
  scale_x_continuous(breaks=c(1960, 1980, 2000))
@

<<CD_GDP_Spaghetti_Graphs_CN, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="CN Cobb-Douglas fitted models.">>=
cdFittedDataCN <- subset(AllFitted, subset = model=="cd" & Country=="CN")
spaghettiPlot(data=cdFittedDataCN, facet_formula=Source~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1960=1)") +
  scale_x_continuous(breaks=c(1960, 1980, 2000))
@

<<CD_Residual_Plot, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="Cobb-Douglas Residual Plots.">>=
# Use residuals_df to make a graph.
cd_residuals_df <- subset(residuals_df, subset = modelType=="cd")
ggplot(data=cd_residuals_df, aes(x=year, y=resid, color=Source)) + 
  geom_point(size = 1.0) +
  facet_grid(Country ~ energyType) +
  labs(x = "", y = "Residuals") + 
  xy_theme()
@

@@

Coefficients for each resampled CES model for all countries and all nests
are shown in 
Figures~\ref{fig:CES_lambda_gamma_graph_X}--\ref{fig:CES_sigma_delta_graph_X}. 
The white crosshair on each graph shows the location 
of the fit to historical data. 
In Figures~\ref{fig:CES_sigma1_delta1_graph_X} and~\ref{fig:CES_sigma_delta_graph_X},
the bottom of the vertical axis represents $\sigma = 0$.
The top of the vertical axis represents $\sigma = \infty$.

Note that as $\delta$ or $\delta_1$ approaches 0 (1) 
in Equations~\ref{eq:CES}--\ref{eq:CESekl},
the corresponding value of $\sigma$ or $\sigma_1$ becomes irrelevant, and
resample points along the left (right) edge of
Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}
are equivalent.
That is, all points along the left (right) edge of
Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}
have the same $sse$. 
As a consequence, 
the \texttt{cesEst} fitting algorithm has no way 
to discriminate among points along the left (right) edge of
Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}. 
Thus, resample point estimates where $\delta$ or $\delta_1$ approaches 0 (1)
tend to cluster at the locations of the initial grid search in 
$\sigma$ or $\sigma_1$
(0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100).

<<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.0, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with primary exergy ($x_p$).">>=
cesCoeffsDataX <- filter(AllCoeffs, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
                                                                      "(iK + iL) + (iXp)", 
                                                                      "(iL + iXp) + (iK)", 
                                                                      "(iXp + iK) + (iL)"))
standardScatterPlot(data=cesCoeffsDataX, mapping=aes(x=gamma_coef, y=lambda, color=Source), 
                    facet_formula=country~nestStrParen, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    labs(x=expression(gamma), y=expression(lambda)) + 
    guides(colour=guide_legend(override.aes = aes(alpha=1)))
@

<<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with primary exergy ($x_p$).">>=
standardScatterPlot(data=cesCoeffsDataX, mapping=aes(x=delta_1, y=sigma_1, color=Source), 
                    facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1])) + 
    guides(colour=guide_legend(override.aes = aes(alpha=1)))
@

<<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=6, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using primary exergy ($x_p$).">>=
standardScatterPlot(data=subset(cesCoeffsDataX, nestStrParen != "(iK + iL) + ()"),
                    mapping=aes(x=delta, y=sigma, color=Source), 
                    facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma)) +
    guides(colour=guide_legend(override.aes = aes(alpha=1)))
@

@@

Figure~\ref{fig:CES_ternary_graph} shows 
$\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.
Figure~\ref{fig:CES_ternary_graph} is comparable to
the ternary graph for the Cobb-Douglas models, 
Figure~\ref{fig:CD_Ternary_Scatter_Graph}.

<<CES_ternary_graphX, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
standardTriPlot(data=cesCoeffsDataX, 
                mapping=aes(color=Source), 
                facet_formula=country~nestStrParen) +
  guides(colour=guide_legend(override.aes = aes(alpha=1)))
@

% Figure~\ref{fig:CES_Spaghetti_Graph} compares CES model predictions 
% to historical data for all nestings. 
% As with the Cobb-Douglas results, 
% historical data are shown as a black line, 
% the fit to historical data is shown as a white line, and 
% the gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
% 
% <<CES_Spaghetti_Graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with exergy ($x$).", eval=FALSE>>=
% cesFittedDataX <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
%                                                                       "(iK + iL) + (iX)", 
%                                                                       "(iL + iX) + (iK)", 
%                                                                       "(iX + iK) + (iL)"))
% spaghettiPlot(data=cesFittedDataX, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
%     labs(y="Indexed GDP (1900=1 or 1950=1)")
% @
% 
% <<CES_lambda_gamma_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
% cesCoeffsDataU <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
%                                                                       "(iK + iL) + (iU)", 
%                                                                       "(iL + iU) + (iK)", 
%                                                                       "(iU + iK) + (iL)"))
% standardScatterPlot(data=cesCoeffsDataU, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
%     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
%     labs(x=expression(gamma), y=expression(lambda))
% @
% 
% <<CES_sigma1_delta1_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
% standardScatterPlot(data=cesCoeffsDataU, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
%     coord_trans(y="sigma") +
%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
%     labs(x=expression(delta[1]), y=expression(sigma[1]))
% @
% 
% <<CES_sigma_delta_graph_U, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
% standardScatterPlot(data=subset(cesCoeffsDataU, nestStrParen != "(iK + iL) + ()"),
%                     mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
%     coord_trans(y="sigma") +
%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
%     labs(x=expression(delta), y=expression(sigma))
% @
% 
% <<CES_Spaghetti_Graph_U, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with useful work ($u$).", eval=FALSE>>=
% cesFittedDataU <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
%                                                                       "(iK + iL) + (iU)", 
%                                                                       "(iL + iU) + (iK)", 
%                                                                       "(iU + iK) + (iL)"))
% spaghettiPlot(data=cesFittedDataU, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
%     labs(y="Indexed GDP (1900=1 or 1950=1)")
% @

>>>>

# Load models
REXS1960_Models <- loadPostProcessedData(Source = "REXS1960", kind = "models", dir=pp_path)
IST_Models <- loadPostProcessedData(Source = "IST", kind = "models", dir=pp_path)
Leeds_Models <- loadPostProcessedData(Source = "Leeds", kind = "models", dir=pp_path)
AllModels <- unlist(list(REXS1960_Models, IST_Models, Leeds_Models), recursive=FALSE)
# The function to extract data from the models
extract_data <- function(x, name) {
  # Names are in the form Source.Country.modelType.factor_string
  # Parse various pieces of name
  name_pieces <- strsplit(name, split=".", fixed=TRUE)[[1]]
  Source <- name_pieces[[1]]
  Country <- name_pieces[[2]]
  modelType <- name_pieces[[3]]
  factorString <- name_pieces[[4]]
  # Parse the factorString to get the energyType
  energyType <- parseFactorString(factorString)$energyType

  data.frame(year = (attr(x, which="data"))$Year, resid = resid(x), name=name, Source=Source, Country=Country,
             modelType=modelType, factorString=factorString, 
             nestStrParen=parseFactorString(factorString)$nestStrParen, energyType=energyType)
}
residual_data <- leaf_apply(AllModels, extract_data, class=c("CDEmodel", "cesEst", "LINEXmodel"))
# Bind these all in a data frame. 
residuals_df <- do.call(rbind, residual_data)
# Re-order the factors as desired for our graphs.
residuals_df$Source <- as.factor(
  replace(as.character(residuals_df$Source), which(residuals_df$Source=="REXS1960"), "REXS"))
residuals_df$Source <- relevelFactor(residuals_df$Source, levs = c("REXS", "IST", "Leeds"))
residuals_df$energyType <- as.factor(
  replace(as.character(residuals_df$energyType), which(is.na(residuals_df$energyType)), "none"))
residuals_df$energyType <- relevelFactor(as.factor(residuals_df$energyType), levs = energyLevels)
@

@@

<<CD_GDP_Spaghetti_Graphs_UK, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="UK Cobb-Douglas fitted models.">>=
cdFittedDataUK <- subset(AllFitted, subset = model=="cd" & Country=="UK")
spaghettiPlot(data=cdFittedDataUK, facet_formula=Source~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1960=1)") +
  scale_x_continuous(breaks=c(1960, 1980, 2000))
@

<<CD_GDP_Spaghetti_Graphs_JP, fig.pos="H", fig.align='center', fig.width=4, fig.height=2, fig.cap="JP Cobb-Douglas fitted models.">>=
cdFittedDataJP <- subset(AllFitted, subset = model=="cd" & Country=="JP")
spaghettiPlot(data=cdFittedDataJP, facet_formula=Source~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1960=1)") +
  scale_x_continuous(breaks=c(1960, 1980, 2000))
@

@@

<<CD_GDP_Spaghetti_Graphs_PT, fig.pos="H", fig.align='center', fig.width=5, fig.height=2, fig.cap="PT Cobb-Douglas fitted models.">>=
cdFittedDataPT <- subset(AllFitted, subset = model=="cd" & Country=="PT")
spaghettiPlot(data=cdFittedDataPT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1960=1)") +
  scale_x_continuous(breaks=c(1960, 1980, 2000))
@

<<CD_GDP_Spaghetti_Graphs_CN, fig.pos="H", fig.align='center', fig.width=4, fig.height=2, fig.cap="CN Cobb-Douglas fitted models.">>=
cdFittedDataCN <- subset(AllFitted, subset = model=="cd" & Country=="CN")
spaghettiPlot(data=cdFittedDataCN, facet_formula=Source~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1960=1)") +
  scale_x_continuous(breaks=c(1960, 1980, 2000))
@

<<CD_Residual_Plot, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="Cobb-Douglas Residual Plots.">>=
# Use residuals_df to make a graph.
cd_residuals_df <- subset(residuals_df, subset = modelType=="cd")
ggplot(data=cd_residuals_df, aes(x=year, y=resid, color=Source)) + 
  geom_point(size = 1.0) +
  facet_grid(Country ~ energyType) +
  labs(x = "", y = "Residuals") +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) + 
  xy_theme()
@

@@

Coefficients for each resampled CES model for all countries and all nests
are shown in 
Figures~\ref{fig:CES_lambda_gamma_graph_Xp}--\ref{fig:CES_sigma_delta_graph_Xp}. 
The white crosshair on each graph shows the location 
of the fit to historical data. 
In Figures~\ref{fig:CES_sigma1_delta1_graph_Xp} and~\ref{fig:CES_sigma_delta_graph_Xp},
the bottom of the vertical axis represents $\sigma = 0$.
The top of the vertical axis represents $\sigma = \infty$.

Note that as $\delta$ or $\delta_1$ approaches 0 (1) 
in Equations~\ref{eq:CES}--\ref{eq:CESekl},
the corresponding value of $\sigma$ or $\sigma_1$ becomes irrelevant, and
resample points along the left (right) edge of
Figures \ref{fig:CES_sigma1_delta1_graph_Xp} and \ref{fig:CES_sigma_delta_graph_Xp}
are equivalent.
That is, all points along the left (right) edge of
Figures \ref{fig:CES_sigma1_delta1_graph_Xp} and \ref{fig:CES_sigma_delta_graph_Xp}
have the same $sse$. 
As a consequence, 
the \texttt{cesEst} fitting algorithm has no way 
to discriminate among points along the left (right) edge of
Figures \ref{fig:CES_sigma1_delta1_graph_Xp} and \ref{fig:CES_sigma_delta_graph_Xp}. 
Thus, resample point estimates where $\delta$ or $\delta_1$ approaches 0 (1)
tend to cluster at the locations of the initial grid search in 
$\sigma$ or $\sigma_1$
(0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100).

%------------------------------
\subsubsection{CES with primary exergy ($x_p$)} 
\label{sec:ces_xp}
%------------------------------

The following graphs show results for the CES model using primary exergy ($x_p$).

<<CES_lambda_gamma_graph_Xp, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.0, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with primary exergy ($x_p$).">>=
cesCoeffsDataXp <- filter(AllCoeffs, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
                                                                      "(iK + iL) + (iXp)", 
                                                                      "(iL + iXp) + (iK)", 
                                                                      "(iXp + iK) + (iL)"))
standardScatterPlot(data=cesCoeffsDataXp, mapping=aes(x=gamma_coef, y=lambda, color=Source), 
                    facet_formula=country~nestStrParen, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    labs(x=expression(gamma), y=expression(lambda)) + 
    guides(colour=guide_legend(override.aes = aes(alpha=1)))
@

<<CES_sigma1_delta1_graph_Xp, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with primary exergy ($x_p$).">>=
standardScatterPlot(data=cesCoeffsDataXp, mapping=aes(x=delta_1, y=sigma_1, color=Source), 
                    facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1])) + 
    guides(colour=guide_legend(override.aes = aes(alpha=1)))
@

<<CES_sigma_delta_graph_Xp, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=6, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using primary exergy ($x_p$).">>=
standardScatterPlot(data=subset(cesCoeffsDataXp, nestStrParen != "(iK + iL) + ()"),
                    mapping=aes(x=delta, y=sigma, color=Source), 
                    facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma)) +
    guides(colour=guide_legend(override.aes = aes(alpha=1)))
@

@@

Figure~\ref{fig:CES_ternary_graphXp} shows 
$\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.
Figure~\ref{fig:CES_ternary_graphXp} is comparable to
the ternary graph for the Cobb-Douglas models, 
Figure~\ref{fig:CD_Ternary_Scatter_Graph}.

<<CES_ternary_graphXp, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with primary exergy ($x_p$).", eval=TRUE>>=
standardTriPlot(data=cesCoeffsDataXp, 
                mapping=aes(color=Source), 
                facet_formula=country~nestStrParen) +
  guides(colour=guide_legend(override.aes = aes(alpha=1)))
@

Figures~\ref{fig:CES_GDP_Spaghetti_Graph_US_xp}--\ref{fig:CES_GDP_Spaghetti_Graph_CN_xp} 
compare CES model predictions 
to historical data for all nestings, countries, and data sources. 
As with the Cobb-Douglas results, 
historical data are shown as a black line, 
the fit to historical data is shown as a white line, and 
the gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.

<<CES_GDP_Spaghetti_Graph_US_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="US CES with $x_p$ fitted models.">>=
cesFittedDataUS_xp <- subset(AllFitted, subset = model=="ces" & Country=="US" & (energy=="iXp" | energy=="none"))
spaghettiPlot(data=cesFittedDataUS_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1960=1)") +
  scale_x_continuous(breaks=c(1960, 1980, 2000))
@

<<CES_GDP_Spaghetti_Graph_UK_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="UK CES with $x_p$ fitted models.">>=
cesFittedDataUK_xp <- subset(AllFitted, subset = model=="ces" & Country=="UK" & (energy=="iXp" | energy=="none"))
spaghettiPlot(data=cesFittedDataUK_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1960=1)") +
  scale_x_continuous(breaks=c(1960, 1980, 2000))
@

<<CES_GDP_Spaghetti_Graph_JP_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=2.5, fig.cap="JP CES with $x_p$ fitted models.">>=
cdFittedDataJP_xp <- subset(AllFitted, subset = model=="ces" & Country=="JP" & (energy=="iXp" | energy=="none"))
spaghettiPlot(data=cdFittedDataJP_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1960=1)") +
  scale_x_continuous(breaks=c(1960, 1980, 2000))
@

<<CES_GDP_Spaghetti_Graph_AT_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="AT CES with $x_p$ fitted models.">>=
cdFittedDataAT_xp <- subset(AllFitted, subset = model=="ces" & Country=="AT" & (energy=="iXp" | energy=="none"))
spaghettiPlot(data=cdFittedDataAT_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1960=1)") +
  scale_x_continuous(breaks=c(1960, 1980, 2000))
@

<<CES_GDP_Spaghetti_Graph_PT_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=2.5, fig.cap="PT CES with $x_p$ fitted models.">>=
cdFittedDataPT_xp <- subset(AllFitted, subset = model=="ces" & Country=="PT" & (energy=="iXp" | energy=="none"))
spaghettiPlot(data=cdFittedDataPT_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1960=1)") +
  scale_x_continuous(breaks=c(1960, 1980, 2000))
@

<<CES_GDP_Spaghetti_Graph_CN_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=2.5, fig.cap="CN CES with $x_p$ fitted models.">>=
cdFittedDataCN_xp <- subset(AllFitted, subset = model=="ces" & Country=="CN" & (energy=="iXp" | energy=="none"))
spaghettiPlot(data=cdFittedDataCN_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1960=1)") +
  scale_x_continuous(breaks=c(1960, 1980, 2000))
@

<<CES_Residual_Plot, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="CES with $x_p$ Residual Plots.">>=
# Use residuals_df to make a graph.
ces_xp_residuals_df <- subset(residuals_df, subset = modelType=="ces" & (energyType=="iXp" | energyType=="none"))
ggplot(data=ces_xp_residuals_df, aes(x=year, y=resid, color=Source)) + 
  geom_point(size = 1.0) +
  facet_grid(Country ~ nestStrParen) +
  labs(x = "", y = "Residuals") +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) + 
  xy_theme()
@

%------------------------------
\subsubsection{CES with final exergy ($x_f$)} 
\label{sec:ces_xf}
%------------------------------

%------------------------------
\subsubsection{CES with useful work ($u$)} 
\label{sec:ces_u}
%------------------------------

% 
% <<CES_Spaghetti_Graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with exergy ($x$).", eval=FALSE>>=
% cesFittedDataX <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
%                                                                       "(iK + iL) + (iX)", 
%                                                                       "(iL + iX) + (iK)", 
%                                                                       "(iX + iK) + (iL)"))
% spaghettiPlot(data=cesFittedDataX, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
%     labs(y="Indexed GDP (1900=1 or 1950=1)")
% @
% 
% <<CES_lambda_gamma_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
% cesCoeffsDataU <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
%                                                                       "(iK + iL) + (iU)", 
%                                                                       "(iL + iU) + (iK)", 
%                                                                       "(iU + iK) + (iL)"))
% standardScatterPlot(data=cesCoeffsDataU, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
%     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
%     labs(x=expression(gamma), y=expression(lambda))
% @
% 
% <<CES_sigma1_delta1_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
% standardScatterPlot(data=cesCoeffsDataU, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
%     coord_trans(y="sigma") +
%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
%     labs(x=expression(delta[1]), y=expression(sigma[1]))
% @
% 
% <<CES_sigma_delta_graph_U, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
% standardScatterPlot(data=subset(cesCoeffsDataU, nestStrParen != "(iK + iL) + ()"),
%                     mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
%     coord_trans(y="sigma") +
%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
%     labs(x=expression(delta), y=expression(sigma))
% @
% 
% <<CES_Spaghetti_Graph_U, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with useful work ($u$).", eval=FALSE>>=
% cesFittedDataU <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
%                                                                       "(iK + iL) + (iU)", 
%                                                                       "(iL + iU) + (iK)", 
%                                                                       "(iU + iK) + (iL)"))
% spaghettiPlot(data=cesFittedDataU, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
%     labs(y="Indexed GDP (1900=1 or 1950=1)")
% @
